---
title: "Binomial Dist.."
output:
  word_document: default
  pdf_document: default
date: "2024-02-28"
---
1. Let X represent the number of sixes in 10 rolls of a fair die. Simulate 50 runs     of this probability experiment.
2. According to a recent survey 72% of Americans prefer dogs to cats. If 8 Americans are choosen at random, what is the probabilitythat 6 prefer dogs.That fewer than 6 do.
3. A weighted coin has a 42% chance of coming up heads. What is the expected number of heads in 5 tosses. The standard deviation? Consruct a probability histogram for X, the number of heads in 5 tosses.
```{r}
rbinom(50, 10, 1/6)
```



```{r}
table(rbinom(50, 10, 1/6))
```



```{r}
dbinom(6, 8, .72)
```
```{r}
pbinom(5, 8, .72)
```
```{r}
x <- 0:5
x
```
```{r}
p <- dbinom(x, 5, .42)
p
```
```{r}
sum(p)
```
```{r}
weighted.mean(x,p)
```
````{r}
weighted.mean((x-2.1)^2, p)
```
````{r}
weighted.mean((x-2.1)^2, p)^.5
```
````{r}
library(tidyverse)
qplot(x, weight=p, geom ="histogram", bins=6, col=I("black"))
```

``{r}